---
title: "Testing_Data"
author: "Sigurd Fyhn Sørensen"
date: "2022-09-09"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
```


# Introduction
**Steps to follow:**
\- Source/import all the Generative Models/Simulation function. They can all be found in the subfolder called "Simulations".
\- Source/import all the model testing function which can be found in the R script called "ModelFunctions.R" 
\- Once done with step 1 and 2 you can freely simulate data from the different generative models. All models can be tested with empirical and simulated data.
\- \- To test empirical data you have to make sure that your data contains columns with the right names and values. 

ID: Unique ID for every individual caller
CallNr: In case a group has several instances of communication. i.e. They start communicating, takes a pause and then initiate another instance of communication.
Group: Different groups communicating. Individuals should not be able to communicate across groups
Onset: The start time for every initiated call.
Offset: The end time for every initiated call.
Latency: The difference between Onset and the previous calls Offset. 
(Duration): The duration of every call, can be found by Duration = Offset - Onset. Not required for all models but is very useful. 




# Testing of Models

## Testing Simulated Data
```{r}
### Testing Inhibiton

#There are some issues with sizes of two data frames sometimes not matching... Should be looked at..
df_list_inhib <- list()
for (i in 1:10){
  Start <- Sys.time()
  df_list_inhib[[i]] <- InhibitionModel(n = 100, mu_latency = 150, sd_latency = 15, mu_duration = 300, sd_duration = 100) %>% 
    mutate(Group = i) %>% 
    mutate(ID = ID*i)
  End <- Sys.time()
  print(End - Start)
}


#Bind all simulated data sets together
Inhibition_Sim <- do.call("rbind", df_list_inhib)

#Test
InhibitionHypothesis(Inhibition_Sim)
```


```{r}
### Testing Reset

#Simulate Several Instances of Reset data.
df_list <- list()
for (i in 1:10){
  Start <- Sys.time()
  df_list[[i]] <- ResetModel(n = 100, mu_latency = 150, sd_latency = 15, mu_duration = 300, sd_duration = 100) %>% 
    mutate(Group = i)
  End <- Sys.time()
  print(End - Start)
}
#Bind all simulated data sets together
Reset_Sim <- do.call("rbind", df_list)

ResetHypothesis2(Reset_Sim)

```




## Testing Empirical Data

#### Whale
```{r}
df_whale <- read_csv(here("Data", "PilotWhales_jensen.csv"))

df_whale_small <- df_whale %>%
  select(BoutLatency, BoutStartTime, BoutEndTime, Duration, bout,ID, Group) %>% 
  rename(Latency = BoutLatency, Onset = BoutStartTime, Offset = BoutEndTime, CallNr = bout)
```


```{r}
ResetHypothesis2(df_whale_small)
```

```{r}
InhibitionHypothesis(df_whale_small)
```

#### Meerkats
https://pubmed.ncbi.nlm.nih.gov/30416063/

**TO DO**
Get information on the variables. I need to know which variable is ID and which is CallNr (initiation of new communication)...

```{r}
library("readxl")
df_Meerkat <- read_excel(here("Data", "Meerkats_demartsev.xlsx"))
names(df_Meerkat) <- gsub(" ", "", names(df_Meerkat))
names(df_Meerkat) <- gsub("#", "", names(df_Meerkat))

df_Meerkat %>% 
  select(starttime, endtime, Group, FocalID,infile) %>% 
  rename(Onset = starttime, Offset = endtime) %>%


unique(df_Meerkat$Group)
unique(df_Meerkat$FocalID)
```

#### Wrens song
**Questions**
1) The current ID columns reports "male" or "female". Is it because we only have two birds, a female and a male? I am currently assuming ID (gender) acts a a unique identifier for each communicator. 

2) I am currently saying that a latency of over 30 is viewed as initation a new conversation. 
```{r}
load(here("Data","wrens_song.rda"))
wrens <- wrens %>%  
  rename(Onset = start, Offset = end) %>% 
  mutate(Latency = Onset - lag(Offset), Duration = Offset - Onset) %>% 
  mutate(NewCall = if_else(Latency > 30 ,1 ,0)) %>%  #Is it one long recording or several small communique combined. 
  mutate(CallNr = 1)
wrens

for (i in 2:nrow(wrens)){
  if (wrens$NewCall[i] == 0){
      wrens$CallNr[i] <- lag(wrens$CallNr)[i]
  }
  else{
    wrens$CallNr[i] <- lag(wrens$CallNr)[i] + 1
  }
}

ResetHypothesis(wrens)

InhibitionHypothesis(wrens)

```
#### Manakins Song
1) Only 1 pair communicating so we can't test Inhibition Hypothesis as this involves shuffling pairs. 
2) Questions about the ID column again. 
```{r}
load(here("Data","manakins_song.rda"))
manakins <- manakins %>%  
  rename(Onset = start, Offset = end) %>% 
  mutate(Latency = Onset - lag(Offset), Duration = Offset - Onset) %>% 
  mutate(NewCall = if_else(Latency > 30 ,1 ,0)) %>%  #Is it one long recording or several small communique combined. 
  mutate(CallNr = 1)

ResetHypothesis(manakins)
```
#### Chickadees
1) This is communication between a bird and an "audio recording of a bird". 

2) Only 1 pair communicating so we can't test Inhibition Hypothesis as this involves shuffling pairs. 
```{r}
load(here("Data","chickadees_song.rda"))

chickadees <- chickadees %>%  
  rename(Onset = start, Offset = end) %>% 
  mutate(Latency = Onset - lag(Offset), Duration = Offset - Onset) %>% 
  mutate(NewCall = if_else(Latency > 30 ,1 ,0)) %>%  #Is it one long recording or several small communique combined. 
  mutate(CallNr = 1)

ResetHypothesis(chickadees)

```

