---
title: "Testing_Data"
author: "Sigurd Fyhn Sørensen"
date: "2022-09-09"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Introduction
**Steps to follow:**
\- Source/import all the Generative Models/Simulation function. They can all be found in the subfolder called "Simulations".
\- Source/import all the model testing function which can be found in the R script called "ModelFunctions.R" 
\- Once done with step 1 and 2 you can freely simulate data from the different generative models. All models can be tested with empirical and simulated data.
\- \- To test empirical data you have to make sure that your data contains columns with the right names and values. 

ID: Unique ID for every individual caller
CallNr: In case a group has several instances of communication. i.e. They start communicating, takes a pause and then initiate another instance of communication.
Group: Different groups communicating. Individuals should not be able to communicate across groups
Onset: The start time for every initiated call.
Offset: The end time for every initiated call.
Latency: The difference between Onset and the previous calls Offset. 
(Duration): The duration of every call, can be found by Duration = Offset - Onset. Not required for all models but is very useful. 


```{r}
### Testing Inhibiton

#There are some issues with sizes of two data frames sometimes not matching... Should be looked at..
df_list_inhib <- list()
for (i in 1:10){
  Start <- Sys.time()
  df_list_inhib[[i]] <- InhibitionModel(n = 100, mu_latency = 150, sd_latency = 15, mu_duration = 300, sd_duration = 100) %>% 
    mutate(Group = i) %>% 
    mutate(ID = ID*i)
  End <- Sys.time()
  print(End - Start)
}


#Bind all simulated data sets together
Inhibition_Sim <- do.call("rbind", df_list_inhib)

#Test
InhibitionHypothesis(Inhibition_Sim)
```


```{r}
### Testing Reset

#Simulate Several Instances of Reset data.
df_list <- list()
for (i in 1:10){
  Start <- Sys.time()
  df_list[[i]] <- ResetModel(n = 100, mu_latency = 150, sd_latency = 15, mu_duration = 300, sd_duration = 100) %>% 
    mutate(Group = i)
  End <- Sys.time()
  print(End - Start)
}
#Bind all simulated data sets together
Reset_Sim <- do.call("rbind", df_list)

ResetHypothesis2(Reset_Sim)

```