---
title: "Whale Try"
author: "Sigurd Fyhn Sørensen"
date: '2022-06-17'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(rethinking)
library(rstan)
```

```{r}
df_whale <- read_csv("../Data/PilotWhales_jensen.csv")
```
### Plot and investigate the Data
```{r}
pacman::p_load("lubridate")

ggplot(df_whale, aes(xmin = StartTime, xmax = StartTime + Duration )) + geom_rect()
```
# Reset Hypothesis
We will compare the distribution of inter- (between two or more people) vs intra-individual (consecutive solo calls) latencies. 
No difference between the two latency distributions would support the notion of a reset hypothesis.

```{r}
df_whale <- df_whale %>% 
  arrange(StartTime) %>%
  mutate(Interindividual = 0)
  
for(i in 2:nrow(df_whale)){
    df_whale[i,"Interindividual"] = ifelse(df_whale$ID[i] == df_whale$ID[i-1], 0, 1) #Check if inter- or intra-timing
}
df_whale <- df_whale %>% 
    mutate(Interindividual = as.factor(Interindividual))
```


```{r}
#Exploratory stats and plot
df_whale %>% 
  filter(CallType == "ResponseCall") %>%
  count(Interindividual)

df_whale %>% 
  filter(CallType == "ResponseCall") %>%
  ggplot(aes(x= BoutLatency, color = Interindividual)) + geom_density()
```
We have negative values (due to overlapping/interuption) which makes log() transformation difficult unless we work with complex numbers.   

### Comparing Distributions
**Z-score test** http://homework.uoregon.edu/pub/class/es202/ztest.html
```{r}
df_whale %>%
  filter(CallType == "ResponseCall") %>% 
  group_by(Interindividual) %>%
  summarize(mean = mean(BoutLatency), SEM = sd(BoutLatency)/n(),n = n()) %>% 
  summarize(Z_score = (mean[2] - mean[1]) / sqrt(sum(SEM^2)) )
```

### Kolmogorov-Smirnov test (non-parametric)

https://stat.ethz.ch/R-manual/R-patched/library/stats/html/ks.test.html
```{r}
df_whale_Inter <- df_whale %>% 
  filter(CallType == "ResponseCall" & Interindividual == 1) 
df_whale_Intra <- df_whale %>%
  filter(CallType == "ResponseCall" & Interindividual == 0)
  

ks.test(df_whale_Inter$BoutLatency, df_whale_Intra$BoutLatency)
```
We reject the null hypothesis in support of the two distributions being different. 
I.e. We cannot accept the reset hypothesis since the distribution of intra- and inter-individual latency does not originate from the same distribution.




# Test overlap
```{r}
df_whale <- read_csv("../Data/PilotWhales_jensen.csv")
d_list <- list()
Start <- Sys.time();
  
for (i in seq(1000)){
  #print(i)
    d_list[[i]] <- RotateData(d, threshold = threshold, delay = delay) %>%
      mutate(Rotation = i)
}
dRotated <- do.call("rbind", d_list)
End <- Sys.time() # Time to run

write_csv(dRotated, "dRotated.csv")
```

```{r}
dRotated <- read_csv("dRotated.csv")
```


## Permutation
```{r}
dens(df_whale$BoutLatency)

df_whale %>% 
  filter(!is.na(BoutLatency)) %>% 
  summarise(sum(BoutLatency > 0 )/length(BoutLatency))


t.test(df_whale$BoutLatency , mu = 0)
```


