---
title: "Whale Try"
author: "Sigurd Fyhn Sørensen"
date: '2022-06-17'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(rethinking)
library(rstan)
library(here)
```

```{r}
df_whale <- read_csv(here("Data", "PilotWhales_jensen.csv"))
```
### Plot and investigate the Data
```{r}
pacman::p_load("lubridate")

#ggplot(df_whale, aes(xmin = StartTime, xmax = StartTime + Duration )) + geom_rect()
```
# Reset Hypothesis
We will compare the distribution of inter- (between two or more people) vs intra-individual (consecutive solo calls) latencies. 
No difference between the two latency distributions would support the notion of a reset hypothesis.

```{r}
df_whale <- df_whale %>% 
  arrange(StartTime) %>%
  mutate(Interindividual = 0)
  
for(i in 2:nrow(df_whale)){
    df_whale[i,"Interindividual"] = ifelse(df_whale$ID[i] == df_whale$ID[i-1], 0, 1) #Check if inter- or intra-timing
}
df_whale <- df_whale %>% 
    mutate(Interindividual = as.factor(Interindividual))
```


```{r}
#Exploratory stats and plot
df_whale %>% 
  filter(CallType == "ResponseCall") %>%
  count(Interindividual)

df_whale %>% 
  filter(CallType == "ResponseCall") %>%
  ggplot(aes(x= BoutLatency, color = Interindividual)) + geom_density()

df_whale %>% 
  filter(CallType == "ResponseCall") %>%
  ggplot(aes(x= BoutLatency, fill = Interindividual)) + geom_histogram() + facet_wrap(~Interindividual)
```
We have negative values (due to overlapping/interuption) which makes log() transformation difficult unless we work with complex numbers.   

### Comparing Distributions
**Z-score test** http://homework.uoregon.edu/pub/class/es202/ztest.html
```{r}
df_whale %>%
  filter(CallType == "ResponseCall") %>% 
  group_by(Interindividual) %>%
  summarize(mean = mean(BoutLatency), SEM = sd(BoutLatency)/n(),n = n()) %>% 
  summarize(Z_score = (mean[2] - mean[1]) / sqrt(sum(SEM^2)) )
```

### Kolmogorov-Smirnov test (non-parametric)

https://stat.ethz.ch/R-manual/R-patched/library/stats/html/ks.test.html
```{r}
df_whale_Inter <- df_whale %>% 
  filter(CallType == "ResponseCall" & Interindividual == 1) 
df_whale_Intra <- df_whale %>%
  filter(CallType == "ResponseCall" & Interindividual == 0)
  

ks.test(df_whale_Inter$BoutLatency, df_whale_Intra$BoutLatency)
```
We reject the null hypothesis in support of the two distributions being different. 
I.e. We cannot accept the reset hypothesis since the distribution of intra- and inter-individual latency does not originate from the same distribution.


#### Testing it in a bayesian framework.
Possibility of testing it with Stan or something similar if that is preferred.

# Inhibition Hypothesis
• In this test, we exchanged the pairs of callers from different sessions, which generated call exchanges with occasional interruptions (Figure 2B). 
	• Random Pairing outside of ones dyad.

• We then removed the calls that were interrupted (calls with later onsets in the interruptions) and measured the interval distribution between the calls on the simulated sequence (blue line) and compared it
to the real interval distribution (green line).

• If hearing another’s call simply suppressed calls in a production sequence, then
these interval distributions should be the same


## First Way
Here we pair up two whales from different groups into dyads. We order their bouts in order of their start time (Should this be bout number, boutStart or StartTime, each has its merrit). We then calculate new bout latencies. 

TO DO: we need to figure out if it is a response call or initation call?
 \- I am not quite sure how that was achieved. Is it timing depended? 
 \- Consecutive intraindividual call were also coded as response calls in the original data. Is this ok?
 \- Currently I arrange the new "simulated" data by Bout Start time. Is this ok or should it also be arranged by Bout number? 
```{r}
whale_group <- sample(unique(df_whale$Group))

i = 1

for (g in whale_group){
  whale_ID <- sample(unique(filter(df_whale, Group == g)$ID))
  
  for (b in whale_ID){
    #Whale 1
    t1 <- filter(df_whale, Group == g & ID == b)
    
    #Whale 2
    ID_temp <- sample(filter(df_whale, Group != g & ID != b)$ID,1) #Get another whale from a different group.
    
    t2 <- filter(df_whale, ID == ID_temp) #Whale 2
    
    #sanity check!
    print(c(unique(t2$ID), unique(t1$ID)))
    
    #Add new group number
    df_inhib <- rbind(t1,t2) %>% 
      mutate(Group = i)
    
    # df_inhib %>% 
    #   summarize(unique(ID)) %>% 
    #   print()
    
    #Filter interuptung calls and calculate new BoutLatency
    df_inhib <- df_inhib %>% 
      filter(BoutLatency > 0.1) %>% 
      arrange(BoutStartTime) %>% 
      mutate(BoutLatency = BoutStartTime - lag(BoutEndTime, 1))
    
    #Combine
    if (i == 1) df_inhib_final <- df_inhib
    else df_inhib_final <- rbind(df_inhib, df_inhib_final)
    
    i = i + 1
  }
}


```

```{r}
#Check all groups has two unique persons.
df_inhib_final %>% 
  group_by(Group) %>% 
  summarise(unique(ID)) %>%
  count(Group)
```

```{r}
#Combine the simulated and real data
df_inhib_final$Type <-  "Simulated" 
df_whale$Type <-  "Real"

df_inhib_combined <- rbind(df_inhib_final, df_whale)
```

#### Compare the simulated and real BoutLatency Distribution.

```{r}
Plot_inhib1 <- df_inhib_combined %>% 
  ggplot(aes(BoutLatency, color = Type)) + geom_density() + xlim(-10,80) + ggtitle("Method 1")
Plot_inhib1
```

```{r}
ks.test(df_inhib_final$BoutLatency, df_whale$BoutLatency)
```
We reject the null hypothesis of the two distribution being similar. Supporting the hypothesis of the two distributions being different.

**Again Could be done in a bayesian framework using Stan**
  \- this is just an early easy test. 


## Second Way
Whale1 = Find specific bout communicated by specific Whale in a specific Group.
Whale2 = Must not be the same bout in the same group. As this would be matching whale1 with someone from its original communication. It can be any other Bout either in the same group or in another group. 

**LET US DISCUSS THIS:** 
\- (I am unsure if we wanna match the same whale twice but in different bouts, LETS DISCUSS)
\- Another option is also to include several whales in group to get some shuffeld data closer to the original data?
```{r}
i = 1
for (g in unique(df_whale$Group)) {
  
  for (id in unique(df_whale$ID[df_whale$Group == g])){
  
    for (b in (unique(df_whale$bout[df_whale$Group == g & df_whale$ID == id]))){
      
      #Whale1
      whale1 <- subset(df_whale, Group == g & ID == id & bout == b)
      
      #Whale 2
      whale2_INFO <- df_whale %>% 
        group_by(ID, Group, bout) %>% 
        slice_sample()%>% 
        filter(Group != g & ID != id & bout != b) %>%
        ungroup() %>% 
        sample_n(1)

      whale2 <- subset(df_whale, Group == whale2_INFO$Group & ID == whale2_INFO$ID & bout == whale2_INFO$bout)
      
      df_inhib2 <- rbind(whale1,whale2) %>% 
        filter(BoutLatency > 0.1) %>% 
        arrange(BoutStartTime) %>% 
        mutate(Group = i) %>% 
        mutate(BoutLatency = BoutStartTime - lag(BoutEndTime, 1))
    
      
    
    #Combine
    if (i == 1) df_inhib_final2 <- df_inhib2
    else df_inhib_final2 <- rbind(df_inhib2, df_inhib_final2)
      
    i = i +1
    }
  } 
}
```

**Compare**
```{r}
#Combine the simulated and real data
df_inhib_final2$Type <-  "Simulated" 
df_whale$Type <-  "Real"

df_inhib_combined2 <- rbind(df_inhib_final2, df_whale)
```

#### Compare the simulated and real BoutLatency Distribution.

```{r}
Plot_inhib2 <- df_inhib_combined2 %>% 
  ggplot(aes(BoutLatency, color = Type)) + geom_density() + xlim(-10,80) + ggtitle("Method 2")
Plot_inhib2
```

```{r}
ks.test(df_inhib_final$BoutLatency, df_whale$BoutLatency)
```


### Comparing 1st and 2nd method
```{r}
pacman::p_load(ggpubr)
ggarrange(Plot_inhib1, Plot_inhib2, nrow = 2)
```

## Third Way
1. Subset each bout in each group.
2. Check if that bout latency is below 0.1 (interuption bout).
3. Combine all the overlapping bouts in a data frame.
But here we don't have whales outside of their own group or in a different order. (maybe Riccardo can figure out what he did here)
```{r}
df_whale <- read_csv(here("Data", "PilotWhales_jensen.csv"))
rm(OverlappingBouts)

for (g in unique(df_whale$Group)) {
  
  for (b in unique(df_whale$bout[df_whale$Group == g])) {
  
    t <- subset(df_whale, Group == g & bout == b)
    
    if ( sum( t$BoutLatency < 0.1, na.rm = T ) > 0) { #If there exist Bout Latency which is below 0.1, ELSE DISREGARD
      
      if (exists("OverlappingBouts")) {
        OverlappingBouts <- rbind(OverlappingBouts, t)
      } 
      else {
        OverlappingBouts = t
      }
    }
  }
}

OverlappingBoutsSurrogate <- subset(OverlappingBouts, BoutLatency > 0.1 | is.na(BoutLatency)) #Subset again

OverlappingBoutsSurrogate <- OverlappingBoutsSurrogate %>% mutate( 
    BoutLatency = BoutStartTime - lag(BoutEndTime, 1),
  )
OverlappingBoutsSurrogate$BoutLatency[OverlappingBoutsSurrogate$BoutStartTime == 0] <- NA

OverlappingBouts$Type <- "Real"
OverlappingBoutsSurrogate$Type <- "Surrogate"

dO <- rbind(OverlappingBouts, OverlappingBoutsSurrogate)
```

# Coupled Oscillators:
• That is, we measured the interval between marmoset 1’s first call and then the marmoset 20s first, second, third. nth calls. We then repeated this for marmoset 1’s second call. 

• Using this procedure, we quantified the degree of coupling by calculating the cross-correlation between the call time series of the two marmosets exchanging vocalizations. 
 \- Should this be 

If the two marmosets are coupled, then the correlation should have significant peaks at regular intervals

**Assumptions**

\- When working with inter individual communication larger than dyads:
     \- View everyone else than "A" as a collective "B". 

```{r}
InterCallsIntervals <- NULL
for (g in unique(df_whale$Group)){
  for (b in unique(d$bout[df_whale$Group == g])){
  
  Caller1 <- df_whale$WhaleID[df_whale$bout==b & df_whale$Group == g][1] #Identify the first caller
  Calls1 <- df_whale$BoutStartTime[df_whale$bout==b & df_whale$WhaleID == Caller1 & df_whale$Group == g] #All Caller1 calls. 
  
  if (length(df_whale$WhaleID[df_whale$bout==b & df_whale$WhaleID != Caller1 & df_whale$Group == g]>0)){ #All other calls in that specific Bout and Group not produced by Caller1. 
    
    for (call in Calls1){
      #Intercall timings.
      tempIntervals <- df_whale$BoutStartTime[df_whale$bout==b & df_whale$WhaleID != Caller1 & df_whale$Group == g] - call
      #Caller Info
      tempCaller <- df_whale$WhaleID[df_whale$bout==b & df_whale$WhaleID != Caller1 & df_whale$Group == g] 
      Bout <- df_whale$bout[df_whale$bout==b & df_whale$WhaleID != Caller1 & df_whale$Group == g]
      FirstCall <- which(Calls1==call)
      tempData <- data.frame(Intervals = tempIntervals, FirstCaller= Caller1, Caller=tempCaller, Bout = Bout, FirstCall=FirstCall, Group = g)
      
      tempData <- subset(tempData, Intervals > 0) #NOTE NOTE NOTE I AM NOT SURE WE SHOULD DO THIS IF WE WANNA LOOK AT CROSS-CORELATION. 
      
      if (exists("InterCallsIntervals")){
        InterCallsIntervals = rbind(InterCallsIntervals,tempData)
        } 
      else {
        InterCallsIntervals = tempData
        }
      }
    }
  }
}
```

```{r}
InterCallsIntervals <- InterCallsIntervals %>% 
  mutate_at(c("Bout", "FirstCall", "Group", "Caller", "FirstCaller"), as.factor) %>% 
  group_by(Bout, FirstCall, Group) %>% 
  mutate(Index = row_number())
```



```{r}
for (g in unique(InterCallsIntervals$Group)){
  for (b in unique(InterCallsIntervals$Bout[InterCallsIntervals$Group == g])) {
    plot(Intervals ~ x, col = FirstCall, type = "l", data = filter(InterCallsIntervals, Group == g, Bout == b))
    lines(Intervals~x, col = FirstCall, data = filter(InterCallsIntervals, Group == g, Bout == b))
  }
}

```

```{r}
for (g in unique(InterCallsIntervals$Group)){
  for (b in unique(InterCallsIntervals$Bout[InterCallsIntervals$Group == g])) {
    plot(NULL, xlim = c(0,30), ylim = c(0,200))
    lines(Intervals~x, col = FirstCall, data = filter(InterCallsIntervals, Group == g, Bout == b))
  }
}

```

```{r}
InterCallsIntervals %>% 
  ggplot(aes(x = x, y = Intervals, col = FirstCall)) + geom_line()  + facet_grid(rows = vars(Group), cols = vars(Bout))
```
```{r}
pacman::p_load(ggforce)
```


```{r}
p <- InterCallsIntervals %>% 
    ggplot(aes(x = x, y = Intervals, col = FirstCall)) + geom_line()  + facet_wrap_paginate(vars(Bout, Group), nrow = 3, ncol = 1, page = i) + theme(legend.position = "none")

for(i in 1:n_pages(p)){
    p_save <-  p + facet_wrap_paginate(vars(Bout, Group), nrow = 3, ncol = 1, page = i)
  ggsave(plot = p_save, filename = paste0('../Plots/Coupled_Oscillators_page_', i, '.jpg'))
}

```


```{r}
ccf(x = InterCallsIntervals$Intervals[])
```








# Test overlap

Random stuff just exploratory for now. 
```{r}
df_whale <- read_csv(here("Data", "PilotWhales_jensen.csv"))
d_list <- list()
Start <- Sys.time();

for (i in seq(1000)){
  #print(i)
    d_list[[i]] <- RotateData(d, threshold = threshold, delay = delay) %>%
      mutate(Rotation = i)
}
dRotated <- do.call("rbind", d_list)
End <- Sys.time() # Time to run

write_csv(dRotated, "dRotated.csv")
```

```{r}
dRotated <- read_csv("dRotated.csv")
```


## Permutation
```{r}
dens(df_whale$BoutLatency)

df_whale %>% 
  filter(!is.na(BoutLatency)) %>% 
  summarise(sum(BoutLatency > 0 )/length(BoutLatency))


t.test(df_whale$BoutLatency , mu = 0)
```


