---
title: "PilotWhalesTurnTakingAnalysis"
author: "ERHK_RF"
date: "10/5/2019"
output: html_document
---

```{r setup, include =FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Analysis of pilot whales turn taking

Goals of the script:
* Preprocess data
* Assess presence of turn-taking via rotation analysis


# TO DO
## Report the rotated analysis / hyp testing in outcome scale
## Reset and inhibition hypotheses on full dataset
## Implement coupled oscillators
## Poisson processes
## ??Permutation test (replacing one whale from a group with a whale from another)
## ?? Permutation test with removal of 1 individual



```{r Load libraries and data}
## Load the libraries
pacman::p_load(tidyverse,
               brms,
               here)
```


```{r Load libraries and data}
# Define the threshold below which a call is a response call 
threshold <- 100 # 100 is a result from a mixture gaussian model from Frants
# Define max delay (in seconds) for rotation test
delay <- 20

## Function to preprocess the data
CleanData <- function(filename =filename, threshold=threshold){
  
  # Load dataset
  d <- read_delim(filename, "\t") %>% 
  rename( ## More meaningful names to me
    StartTime = Time,
    WhaleID = Source_code,
    WhaleType = Source_type) %>% 
  mutate( # Calculating some additional variables 
    EndTime = StartTime + Duration, 
    Latency = StartTime - lag(EndTime, 1),
    DurationPrev = lag(Duration,1),
    CallType = ifelse(Latency < threshold,"ResponseCall","InitiationCall"),
    Age = ifelse(WhaleType == "Juvenile", 1, ifelse(WhaleType == "Indeterminate",2,3))
  )
  
  ### Identifying bouts by identifying initiating calls (calls with > threshold of distance from previous calls)
  
  b <- 1 # initializing bout counter
  d$bout[1] <- 1 # first data point belongs to first bout 
  
  for (n in c(2:nrow(d))){
    
    if (d$Latency[n] > threshold){
      b <- b + 1 # if the distance from previous call is higher than the threshold, change bout
      }
    d$bout[n] <- b # add bout counter value
  }
  
  ## Remove duplicates due to multiple recording devices
  dups =NULL
  for (i in 2:nrow(d)){
    
    if (d$bout[i]==d$bout[i-1] & d$WhaleID[i]==d$WhaleID[i-1] & d$StartTime[i] - d$StartTime[i-1] < 1 & d$Focal[i]!=d$Focal[i-1]){
      dups <- append(dups,i)
    }
    
  }
  
  if (length(dups)){
    d <- d[-dups,]
  }
  
  d <- d %>% 
  mutate(
    Latency = StartTime - lag(EndTime, 1),
    )
  
  d_Real <- d
  
  for (i in unique(d_Real$bout)){
    ## Let's reset the timer within each bout
    BoutReset <- d_Real$StartTime[d_Real$bout==i][1]
    d_Real$BoutStartTime[d_Real$bout==i] <- d_Real$StartTime[d_Real$bout==i] - BoutReset
    d_Real$BoutEndTime[d_Real$bout==i] <- d_Real$EndTime[d_Real$bout==i] - BoutReset
  }
  
  d_Real <- d_Real %>% mutate(
    BoutLatency = BoutStartTime - lag(BoutEndTime, 1),
  )
  
  d_Real$Type <- "Real"
  
  d_Real$BoutLatency[d_Real$BoutStartTime == 0]<-NA
  
  return(d_Real)
}

RotateData <- function(d = data, threshold = threshold, delay = delay) {

  # We create rotated datasets
  ## for each whale but the first we add a random n of seconds to the timeseries of starting points
  ## we take the shifted timeseries which are now longer than the bout and we cut and paste the sticking out bit to the beginning
  
  for (i in unique(d$bout)){
    
    ## Let's reset the timer within each bout
    BoutReset <- d$StartTime[d$bout==i][1]
    d$BoutStartTime[d$bout==i] <- d$StartTime[d$bout==i] - BoutReset
    d$BoutEndTime[d$bout==i] <- d$EndTime[d$bout==i] - BoutReset
    
    ## identify all callers but the first
    Callers <- unique(d$WhaleID[d$bout==i])
    RotatedCallers <- Callers[-1]
    RotatedDelays <- runif(length(RotatedCallers), min= 1, max= delay)
    
    ## Last call
    LastCall <- nrow(d[d$bout==i,])
    BoutEnd <- d$BoutEndTime[d$bout==i][LastCall]
    
    if (length(Callers)>1){
      
      for (n in seq(length(RotatedCallers))){
        
        rc <- RotatedCallers[n]
        
        d$BoutStartTime[d$bout==i & d$WhaleID == rc] <- d$BoutStartTime[d$bout==i & d$WhaleID == rc] + RotatedDelays[n]
        d$BoutEndTime[d$bout==i & d$WhaleID == rc] <- d$BoutEndTime[d$bout==i & d$WhaleID == rc] + RotatedDelays[n]
        
        d$BoutStartTime[d$bout==i & d$WhaleID == rc & d$BoutStartTime > BoutEnd] <- d$BoutStartTime[d$bout==i & d$WhaleID == rc & d$BoutStartTime > BoutEnd] - BoutEnd
        
        d$BoutEndTime[d$bout==i & d$WhaleID == rc & d$BoutEndTime > BoutEnd] <- d$BoutStartTime[d$bout==i & d$WhaleID == rc & d$BoutEndTime > BoutEnd] + d$Duration[d$bout==i & d$WhaleID == rc & d$BoutEndTime > BoutEnd ]
        
      }
      
    }
    
  }
  
  d <-d[order(d$bout, d$BoutStartTime),]
  
  d <- d %>% mutate(
    BoutLatency = BoutStartTime - lag(BoutEndTime, 1),
  )
   d$BoutLatency[d$BoutStartTime == 0]<-NA
  
  d$Type <- "Rotated"
  
  d <- d[order(d$StartTime),]
  d <- d %>% 
    mutate(
      Latency = StartTime - lag(EndTime, 1),
    )
  
 
  
  return(d)
}
```


```{r Load libraries and data}
## Load and preprocess the data
## Now with one dataset
# d1 <- CleanData(
#   filename = "../Data/gm15_257_call_table.txt",
#   threshold = threshold) %>%
#   mutate(
#     Group = "G1",
#     ID = paste0("d1_",WhaleID))
# 
# d2 <- CleanData(
#   filename = "..Data/gm12_224_call_table.txt",
#   threshold = threshold) %>%
#   mutate(
#     Group = "G2",
#     ID = paste0("d2_",WhaleID))
# 
# d3 <- CleanData(
#   filename = "data/gm12_207_call_table.txt",
#   threshold = threshold) %>%
#   mutate(
#     Group = "G3",
#     ID = paste0("d3_",WhaleID))
```


```{r}
# d <- read_csv("../Data/PilotWhales_jensen.csv")
# Start <- Sys.time()
# for (i in seq(1000)){
#   print(i)
#   
#     
#     d <- RotateData(d, threshold = threshold, delay = delay) %>%
#       mutate(Rotation = i)
#     
#     if (exists("dRotated")){dRotated = rbind(dRotated,d)} else {dRotated = d }
# 
# }
# End <- Sys.time()
# End - Start # Time to run
# 
# 
# write_csv(dRotated, "../Data/dRotated.csv")
# dd <- rbind(d, subset(dRotated, select=-Rotation))
```

```{r}
d <- read_csv("../Data/PilotWhales_jensen.csv")
d_list <- list()
Start <- Sys.time();
  
for (i in seq(1000)){
  #print(i)
    d_list[[i]] <- RotateData(d, threshold = threshold, delay = delay) %>%
      mutate(Rotation = i)
}
dRotated <- do.call("rbind", d_list)
End <- Sys.time() # Time to run
End - Start

write_csv(dRotated, "../Data/dRotated.csv")
```



## Testing for change in overlapping in the rotated dataset
```{r}
dRotated <- read_csv("../Data/dRotated.csv")
```


```{r}
# We generate a few different performance measures before comparing how likely real data are in the rotated distribution
### N of overlappings by group
### Duration of overlapping
### Fraction of the call overlapping

RotatedStats <- dRotated %>% group_by(Rotation, Group) %>% #, WhaleID
  summarize(
    OverlappingN = sum(BoutLatency < 0.1, na.rm=T),
    OverlappingProb = sum(BoutLatency < 0.1, na.rm=T)/n(),
    OverlappingDuration = sum(ifelse(BoutLatency < 0.1, abs(BoutLatency), 0), na.rm=T),
    OverlappingFraction = mean(ifelse(BoutLatency < 0.1, abs(BoutLatency)/Duration, NA), na.rm=T),
    OverlappingFraction2 = mean(ifelse(BoutLatency < 0.1, abs(BoutLatency)/Duration, 0), na.rm=T)
  )

Stats <- dRotated %>% group_by(Group) %>% #, WhaleID
  summarize(
    OverlappingN = sum(BoutLatency < 0.1, na.rm=T),
    OverlappingProb = sum(BoutLatency < 0.1, na.rm=T)/n(),
    OverlappingDuration = sum(ifelse(BoutLatency < 0.1, abs(BoutLatency), 0), na.rm=T),
    OverlappingFraction = mean(ifelse(BoutLatency < 0.1, abs(BoutLatency)/Duration, NA), na.rm=T),
    OverlappingFraction2 = mean(ifelse(BoutLatency < 0.1, abs(BoutLatency)/Duration, 0), na.rm=T)
  )

ss <- r

sum(RotatedStats$OverlappingProb[RotatedStats$Group== "G1"] > Stats$OverlappingProb[Stats$Group== "G1"])/nrow(RotatedStats[RotatedStats$Group== "G1",])

sum(RotatedStats$OverlappingProb[RotatedStats$Group== "G2"] > Stats$OverlappingProb[Stats$Group== "G2"])/nrow(RotatedStats[RotatedStats$Group== "G2",])

sum(RotatedStats$OverlappingProb[RotatedStats$Group== "G3"] > Stats$OverlappingProb[Stats$Group== "G3"])/nrow(RotatedStats[RotatedStats$Group== "G3",])

sum(RotatedStats$OverlappingDuration[RotatedStats$Group== "G1"] > Stats$OverlappingDuration[Stats$Group== "G1"])/nrow(RotatedStats[RotatedStats$Group== "G1",])

sum(RotatedStats$OverlappingDuration[RotatedStats$Group== "G2"] > Stats$OverlappingDuration[Stats$Group== "G2"])/nrow(RotatedStats[RotatedStats$Group== "G2",])

sum(RotatedStats$OverlappingDuration[RotatedStats$Group== "G3"] > Stats$OverlappingDuration[Stats$Group== "G3"])/nrow(RotatedStats[RotatedStats$Group== "G3",])

sum(RotatedStats$OverlappingFraction2[RotatedStats$Group== "G1"] > Stats$OverlappingFraction2[Stats$Group== "G1"])/nrow(RotatedStats[RotatedStats$Group== "G1",])

sum(RotatedStats$OverlappingFraction2[RotatedStats$Group== "G2"] > Stats$OverlappingFraction2[Stats$Group== "G2"])/nrow(RotatedStats[RotatedStats$Group== "G2",])

sum(RotatedStats$OverlappingFraction2[RotatedStats$Group== "G3"] > Stats$OverlappingFraction2[Stats$Group== "G3"])/nrow(RotatedStats[RotatedStats$Group== "G3",])

sum(RotatedStats$OverlappingFraction[RotatedStats$Group== "G1"] > Stats$OverlappingFraction[Stats$Group== "G1"])/nrow(RotatedStats[RotatedStats$Group== "G1",])

sum(RotatedStats$OverlappingFraction[RotatedStats$Group== "G2"] > Stats$OverlappingFraction[Stats$Group== "G2"])/nrow(RotatedStats[RotatedStats$Group== "G2",])

sum(RotatedStats$OverlappingFraction[RotatedStats$Group== "G3"] > Stats$OverlappingFraction[Stats$Group== "G3"])/nrow(RotatedStats[RotatedStats$Group== "G3",])
```


## RESET Hypothesis:
### extract intervals btw consecutive calls within bout by the same individual *tagging the individual*
### extract intervals btw consecutive calls within bout by different individuals *tagging the second individual*
### Compare the distributions. Reset says they are the same

```{r}
d$Within <- NA

for (i in 2:nrow(d)){
  
  if (d$bout[i] == d$bout[i-1] & d$ID[i] != d$ID[i-1]){
      d$Within[i] = 0
  } else if ((d$bout[i] == d$bout[i-1] & d$ID[i] == d$ID[i-1])){
      d$Within[i] = 1
    }
    
}

d$Within[d$BoutStartTime == 0] <- NA
d$Within <- as.factor(d$Within)
d$ResetTime <- d$BoutLatency + lag(d$Duration,1)
  
ggplot(d,aes(BoutLatency)) + 
  geom_density(aes(group = ID, fill = ID), alpha= 0.2) +
  facet_wrap(.~ Within)

ggplot(d,aes(BoutLatency)) + 
  geom_density(aes(group = Within, fill = Within), alpha= 0.2) +
  facet_wrap(.~ ID)

ggplot(d,aes(BoutLatency)) + 
  geom_density(aes(group = Within, fill = Within), alpha= 0.2)

ggplot(d,aes(ResetTime)) + 
  geom_density(aes(group = WhaleID, fill = WhaleID), alpha= 0.2) +
  facet_wrap(.~ Within)

ggplot(d,aes(ResetTime)) + 
  geom_density(aes(group = Within, fill = Within), alpha= 0.2) +
  facet_wrap(.~ WhaleID)

ggplot(d,aes(ResetTime)) + 
  geom_density(aes(group = Within, fill = Within), alpha= 0.2)

d %>% group_by(Within) %>% summarize(mean(ResetTime, na.rm=T))

dL <- subset(d, !is.na(BoutLatency) & !is.na(Within) & !is.na(Group) & !is.na(ID) & CallType != "InitiationCall")

# Define formula
BoutEx_f <- bf(BoutLatency ~ 0 + Within + (0 + Within | Group) + (0 + Within | ID),
     beta ~ 0 + Within + (0 + Within | Group) + (0 + Within | ID)# + (0 + Type | bout)
)

# Identify parameters for exgaussian
get_prior(
  BoutEx_f,
  data = d,
  family = exgaussian)

# Define priors
priorEx <- c(
  prior(normal(0,5), class = b),
  prior(normal(0,1), class = sigma),
  prior(normal(0,.5), class = sd),
  prior(normal(0,2), class = sd, group = Group),
  prior(normal(0,2), class = b, dpar = beta),
  prior(normal(0,1), class = sd, dpar = beta),
  prior(normal(0,0.3), class = sd, dpar = beta, group=ID),
  prior(lkj(5), class = cor)
)

# Check prior predictions
ResetLatencyEx_m0 <- brm(
  BoutEx_f,
  data = dL ,
  family = exgaussian,
  prior = priorEx,
  sample_prior = "only",
  file = here("models","ResetLatencyEx_m0"),
  chains = 2,
  cores = 2,
  backend = "cmdstanr",
  threads = threading(2)
  )
pp_check(ResetLatencyEx_m0,ndraws = 100)


# Run the model
ResetLatencyEx_m <- brm(
  BoutEx_f,
  data = dL,
  family = exgaussian,
  prior = priorEx,
  sample_prior = T,
  chains = 2,
  cores = 2,
  iter = 4000,
  file = here("models","ResetLatencyEx_m"),
  backend = "cmdstanr",
  threads = threading(2),
  control = list(
    adapt_delta = 0.99,
    max_treedepth = 20
  )
  )
pp_check(ResetLatencyEx_m,ndraws = 100)

## Check prior/posterior update

plot(hypothesis(ResetLatencyEx_m,"Within0 < 0"))
plot(hypothesis(ResetLatencyEx_m,"Within1 < 0"))
plot(hypothesis(ResetLatencyEx_m,"beta_Within0 < 0"))
plot(hypothesis(ResetLatencyEx_m,"beta_Within1 < 0"))
plot(hypothesis(ResetLatencyEx_m,"sd_Group__Within0 < 0", class = ""))
plot(hypothesis(ResetLatencyEx_m,"sd_Group__Within1 < 0", class = ""))
plot(hypothesis(ResetLatencyEx_m,"sd_Group__beta_Within0 < 0", class = ""))
plot(hypothesis(ResetLatencyEx_m,"sd_Group__beta_Within1 < 0", class = ""))
plot(hypothesis(ResetLatencyEx_m,"sd_ID__Within0 < 0", class = ""))
plot(hypothesis(ResetLatencyEx_m,"sd_ID__Within1 < 0", class = ""))
plot(hypothesis(ResetLatencyEx_m,"sd_ID__beta_Within0 < 0", class = ""))
plot(hypothesis(ResetLatencyEx_m,"sd_ID__beta_Within1 < 0", class = ""))
plot(hypothesis(ResetLatencyEx_m,"sigma < 0", class = ""))

# check summary
summary(ResetLatencyEx_m)

dL$Preds <- predict(ResetLatencyEx_m)[,1]

hypothesis(ResetLatencyEx_m,"Within1-Within0 = 0")
hypothesis(ResetLatencyEx_m,"Within1-Within0 = 0", scope = "coef", group = "Group")
hypothesis(ResetLatencyEx_m,"Within1-Within0 = 0", scope = "coef", group = "ID")

hypothesis(ResetLatencyEx_m,"b_beta_Within1-b_beta_Within0 = 0", class = "")
hypothesis(ResetLatencyEx_m,"beta_Within1-beta_Within0 = 0", class = "b", scope = "coef", group = "Group")

plot(hypothesis(ResetLatencyEx_m,"Within1-Within0 = 0"))
plot(hypothesis(ResetLatencyEx_m,"b_beta_Within1-b_beta_Within0 = 0", class = ""))



  
```



## INHIBITION hypothesis
## we exchanged the pairs of callers from different sessions, which generated call exchanges with occasional interruptions (Figure 2B). 
### We then removed the calls that were interrupted (calls with later onsets in the interruptions)
### we then measured the interval distribution between the calls on the simulated sequence (blue line) and compared it to the real interval distribution (green line). 
## we remove the calls that were interrupted
## measure the interval distribution in surrogate and in real pairs
```{r}

for (g in unique(d$Group)) {
  
  for (b in unique(d$bout[d$Group == g])) {
  
    t <- subset(d, Group == g & bout == b)
    
    if (sum(t$BoutLatency < 0.1, na.rm = T) > 0) {
      if (exists("OverlappingBouts")) {
        OverlappingBouts <- rbind(OverlappingBouts, t)
      } else {
        OverlappingBouts = t
      }
    }
  }
}

OverlappingBoutsSurrogate <- subset(OverlappingBouts, BoutLatency > 0.1 | is.na(BoutLatency)) 

OverlappingBoutsSurrogate <- OverlappingBoutsSurrogate %>% mutate(
    BoutLatency = BoutStartTime - lag(BoutEndTime, 1),
  )
OverlappingBoutsSurrogate$BoutLatency[OverlappingBoutsSurrogate$BoutStartTime == 0] <- NA

OverlappingBouts$Type <- "Real"
OverlappingBoutsSurrogate$Type <- "Surrogate"

dO <- rbind(OverlappingBouts, OverlappingBoutsSurrogate)

ggplot(OverlappingBouts, aes(BoutLatency)) + geom_density()

ggplot(OverlappingBoutsSurrogate, aes(BoutLatency)) + geom_density()


# Define formula
BoutEx_f <- bf(BoutLatency ~ 0 + Type + (0 + Type | Group) + (0 + Type | ID),
     beta ~ 0 + Type + (0 + Type | Group) + (0 + Type | ID)# + (0 + Type | bout)
)

# Identify parameters for exgaussian
get_prior(
  BoutEx_f,
  data = dO,
  family = exgaussian)

# Define priors
priorEx <- c(
  prior(normal(0,5), class = b),
  prior(normal(0,1), class = sigma),
  prior(normal(0,.5), class = sd),
  prior(normal(0,2), class = sd, group = Group),
  prior(normal(0,2), class = b, dpar = beta),
  prior(normal(0,1), class = sd, dpar = beta),
  prior(normal(0,0.3), class = sd, dpar = beta, group=ID),
  prior(lkj(5), class = cor)
)

# Check prior predictions
InhibitionLatencyEx_m <- brm(
  BoutEx_f,
  data = dO ,
  family = exgaussian,
  prior = priorEx,
  sample_prior = T,
  #file = here("models","RotatedLatencyEx_m0"),
  chains = 2,
  cores = 2,
  backend = "cmdstanr",
  threads = threading(2),
  control = list(adapt_delta= 0.99, max_treedepth=20)
  )
pp_check(InhibitionLatencyEx_m,ndraws = 100)

```



## COUPLED OSCILLATORS HYPOTHESES
### 1. PRESENCE OF PERIODIC COUPLINGS
#### CONSISTENT WITHIN CALLER INTERCALL INTERVAL FOR CALLER N
#### NON-OVERLAPPING AND CONSISTENT INTERCALLER INTERCALL INTERVALS FOR OTHER CALLERS

#### TAKE ALL CALLERS BUT THE FIRST, MEASURE INTERCALL INTERVALS FROM FIRST CALLER'S FIRST CALL
####                                 MEASURE INTERCALL INTERVALS FROM FIRST CALLER'S SECOND CALL (ETC)
#### MEASURE THE CROSS-CORRELATION BETWEEN CALL TIME SERIES OF THE TWO MARMOSETS


## Calculate the intercall intervals

```{r}

InterCallsIntervals <- NULL

for (b in unique(d$bout)){
  
  Caller1 <- d$WhaleID[d$bout==b][1]
  Calls1 <- d$BoutStartTime[d$bout==b & d$WhaleID == Caller1]
  
  if (length(d$WhaleID[d$bout==b & d$WhaleID != Caller1]>0)){
    
    for (call in Calls1){
      
      tempIntervals <- d$BoutStartTime[d$bout==b & d$WhaleID != Caller1] - call
      temp1Caller <- Caller1
      tempCaller <- d$WhaleID[d$bout==b & d$WhaleID != Caller1]
      Bout <- d$bout[d$bout==b & d$WhaleID != Caller1]
      FirstCall <- which(Calls1==call)
      tempData <- data.frame(Intervals = tempIntervals, FirstCaller= temp1Caller, Caller=tempCaller, Bout = Bout, FirstCall=FirstCall)
      
      tempData <- subset(tempData, Intervals > 0)
      
      if (exists("InterCallsIntervals")){
        InterCallsIntervals = rbind(InterCallsIntervals,tempData)
      } else {
        InterCallsIntervals = tempData
      }
      
    }
  }
}

ggplot(InterCallsIntervals, aes(Intervals)) + geom_density()
ggplot(subset(InterCallsIntervals, FirstCall== 1), aes(Intervals)) + geom_density()

boutlength = NULL
for (b in unique(d$bout)){
  boutlength = append(boutlength,max(d$BoutEndTime[d$bout==b]))
}


```

# Statistical analysis
We use a exgaussian distribution to describe the latencies between calls


```{r}
dL <- subset(dd, !is.na(BoutLatency) & !is.na(Type) & !is.na(Group) & !is.na(ID) & CallType != "InitiationCall")

BoutEx_f <- bf(BoutLatency ~ 0 + Type + (0 + Type | Group) + (0 + Type | ID),
     beta ~ 0 + Type + (0 + Type | Group) + (0 + Type | ID)# + (0 + Type | bout)
)

# Identify parameters for exgaussian
get_prior(
  BoutEx_f,
  data = d,
  family = exgaussian)

# Define priors
priorEx <- c(
  prior(normal(0,5), class = b),
  prior(normal(0,1), class = sigma),
  prior(normal(0,.5), class = sd),
  prior(normal(0,2), class = sd, group = Group),
  prior(normal(0,2), class = b, dpar = beta),
  prior(normal(0,1), class = sd, dpar = beta),
  prior(normal(0,0.3), class = sd, dpar = beta, group=ID),
  prior(lkj(5), class = cor)
)

# Check prior predictions
RotatedLatencyEx_m0 <- brm(
  BoutEx_f,
  data = dL ,
  family = exgaussian,
  prior = priorEx,
  sample_prior = "only",
  file = here("models","RotatedLatencyEx_m0"),
  chains = 2,
  cores = 2,
  backend = "cmdstanr",
  threads = threading(2)
  )
pp_check(RotatedLatencyEx_m0,ndraws = 100)


# Run the model
RotatedLatencyEx_m <- brm(
  BoutEx_f,
  data = dL,
  family = exgaussian,
  prior = priorEx,
  sample_prior = T,
  chains = 2,
  cores = 2,
  iter = 4000,
  file = here("models","RotatedLatencyEx_m"),
  backend = "cmdstanr",
  threads = threading(2),
  control = list(
    adapt_delta = 0.99,
    max_treedepth = 20
  )
  )
pp_check(RotatedLatencyEx_m,ndraws = 100)

## Check prior/posterior update

plot(hypothesis(RotatedLatencyEx_m,"TypeReal < 0"))
plot(hypothesis(RotatedLatencyEx_m,"TypeRotated < 0"))
plot(hypothesis(RotatedLatencyEx_m,"beta_TypeReal < 0"))
plot(hypothesis(RotatedLatencyEx_m,"beta_TypeRotated < 0"))
plot(hypothesis(RotatedLatencyEx_m,"sd_Group__TypeReal < 0", class = ""))
plot(hypothesis(RotatedLatencyEx_m,"sd_Group__TypeRotated < 0", class = ""))
plot(hypothesis(RotatedLatencyEx_m,"sd_Group__beta_TypeReal < 0", class = ""))
plot(hypothesis(RotatedLatencyEx_m,"sd_Group__beta_TypeRotated < 0", class = ""))
plot(hypothesis(RotatedLatencyEx_m,"sd_ID__TypeReal < 0", class = ""))
plot(hypothesis(RotatedLatencyEx_m,"sd_ID__TypeRotated < 0", class = ""))
plot(hypothesis(RotatedLatencyEx_m,"sd_ID__beta_TypeReal < 0", class = ""))
plot(hypothesis(RotatedLatencyEx_m,"sd_ID__beta_TypeRotated < 0", class = ""))
plot(hypothesis(RotatedLatencyEx_m,"sigma < 0", class = ""))

# check summary
summary(RotatedLatencyEx_m)

# Test hypotheses
dCounter <- data.frame(Type = c("Real","Rotated"), Group = 1000, ID = 100)
Preds <- predict(RotatedLatencyEx_m, newdata = dCounter, allow_new_levels = TRUE)

hypothesis(RotatedLatencyEx_m,"TypeReal-TypeRotated < 0")
hypothesis(RotatedLatencyEx_m,"b_beta_TypeReal-b_beta_TypeRotated < 0", class = "")
ggplot(d,aes(BoutLatency)) + geom_density(aes(group=Type,fill=Type), alpha= 0.2) + theme_classic()

x <- subset(d,BoutLatency<0)
```

## Just looking at overlapping

```{r overlapping analysis}
dL <- dL %>% mutate(
  Overlapping = ifelse(BoutLatency < 0.1, 1, 0)
)

Overlapping_f <- bf(Overlapping ~ 0 + Type + (0 + Type | Group) + (0 + Type | ID))

priorOverlapping <- c(
  prior(normal(0, 2), class = b),
  prior(normal(0, .5), class = sd),
  prior(normal(0, 1), class = sd, group = Group),
  prior(lkj(5), class = cor)
)

# Check prior predictions
RotatedOverlapping_m0 <- brm(
  Overlapping_f,
  data = dL ,
  family = bernoulli(),
  prior = priorOverlapping,
  sample_prior = "only",
  file = here("models","RotatedOverlapping_m0"),
  chains = 2,
  cores = 2,
  backend = "cmdstanr",
  threads = threading(2)
  )

RotatedOverlapping_m <- brm(
  Overlapping_f,
  data = dL ,
  family = bernoulli(),
  prior = priorOverlapping,
  sample_prior = TRUE,
  file = here("models","RotatedOverlapping_m"),
  chains = 2,
  cores = 2,
  backend = "cmdstanr",
  threads = threading(2)
  )
plot(hypothesis(RotatedOverlapping_m, "TypeReal > 0"))
plot(hypothesis(RotatedOverlapping_m, "TypeRotated > 0"))
plot(hypothesis(RotatedOverlapping_m, "TypeRotated > TypeReal"))
plot(hypothesis(RotatedOverlapping_m, "sd_Group__TypeReal > 0", class = ""))
plot(hypothesis(RotatedOverlapping_m, "sd_ID__TypeReal > 0", class = ""))
plot(hypothesis(RotatedOverlapping_m, "sd_Group__TypeRotated > 0", class = ""))
plot(hypothesis(RotatedOverlapping_m, "sd_ID__TypeRotated > 0", class = ""))
Posterior <- posterior_samples(RotatedOverlapping_m)
hypothesis(RotatedOverlapping_m, "TypeRotated = TypeReal")
hypothesis(RotatedOverlapping_m, "TypeRotated < TypeReal")
hypothesis(RotatedOverlapping_m, "TypeRotated > TypeReal")


hypothesis(RotatedOverlapping_m, "TypeRotated = TypeReal", group = "Group", scope = "coef")
```
